test

### 2021-02-18 manuscript/bef_stability/appendixB.Rmd
Sensivity analysis for referee two and three

  params <- sem$coefficients
  colnames(params)[length(colnames(params))] <- "Stars"

@@

kable(format_coef_table(stab_sem_rich),
  format = "latex",
  booktabs = T,
  caption = est_stab_sem_caption
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

kable(format_coef_table(bm_sem_rich),
  format = "latex",
  booktabs = T,
  caption = est_bm_sem_caption
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

>>>>

  params <- sem$coefficients[, -length(colnames(sem$coefficients))]
  #colnames(params)[length(colnames(params))] <- "Stars"

@@

format_coef_table(stab_sem_rich) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
  kable(
    format = "latex",
    booktabs = T,
    caption = est_stab_sem_caption
    ) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```

@@

format_coef_table(bm_sem_rich) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = est_bm_sem_caption
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

### 2021-02-18 manuscript/bef_stability/sem_relationship.Rmd
Sensivity analysis for referee two and three

get_predict_from_model_x <- function (mod = NULL, term = NULL) {
  ggpredict(mod, terms = c(term)) %>%
    as.tibble()
}

@@

# Write plots:
map(stab_plot$gg,
  ~save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      paste0(
	"stab_",
	names(.x$labels$y),
	"_",
	names(.x$labels$x),
	".png"
      )
      ), .x) 
)

@@

# Write plots:
map(bm_plot$gg,
  ~save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      paste0(
	"bm_",
	names(.x$labels$y),
	"_",
	names(.x$labels$x),
	".png"
      )
      ), .x) 
)
mysave(bm_plot, mypath("manuscript", "bef_stability", "result"), overwrite = TRUE)
```

>>>>

get_predict_from_model_x <- function (mod = NULL, term = NULL) {
  ggpredict(mod, terms = c(term)) %>%
    as_tibble()
}

@@

# Write plots:
map(stab_plot$gg,
  ~save_plot(
    file = mypath(
      "manuscript", "bef_stability", "result", 
      paste0(
	"stab_",
	names(.x$labels$y),
	"_",
	names(.x$labels$x),
	".png"
      )
      ),
    plot = .x,
    base_height = 2.5, base_asp = 1.2#1.618 
  ) 
)

@@

# Write plots:
map(bm_plot$gg,
  ~save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      paste0(
	"bm_",
	names(.x$labels$y),
	"_",
	names(.x$labels$x),
	".png"
      )
      ),
    plot = .x,
    base_height = 2.5, base_asp = 1.2#1.618 
    ) 
)
mysave(bm_plot, mypath("manuscript", "bef_stability", "result"), overwrite = TRUE)
```
